---
title: "Vowel Artic in PD: Plots"
output: html_notebook
---

# Packages
```{r}
library(tidyverse)
library(ggrepel)
library(extraDistr)   # install.packages("extraDistr")
library(HDInterval)   # install.packages("HDAPerval")
library(tidybayes)    # install.packages("tidybayes")
library(bayesplot)    # install.packages("bayesplot")
library(modelr)
library(broom.mixed)  # install.packages("broom.mixed")
library(brms)         # install.packages("brms")
library(ggthemes)
library(patchwork)
theme_set(theme_minimal())

# Creating a theme function used for visualizations
theme_clean <- function() {
  theme_minimal(base_family = "Arial") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(face = "bold"),
          axis.title = element_text(face = "bold"),
          strip.text = element_text(face = "bold", size = rel(1), hjust = 0),
          strip.background = element_rect(fill = "grey80", color = NA),
          legend.title = element_text(face = "bold"))
}
```

# Loading the models
```{r}
model_Int <- base::readRDS(file = "Models/brms_Int.rds")
model_AP <- base::readRDS(file = "Models/brms_AP.rds")
model_aVSA <- base::readRDS(file = "Models/brms_aVSA.rds")
model_kinDistance <- base::readRDS(file = "Models/brms_kinDistance.rds")
model_kinDistance_duration <- base::readRDS(file = "Models/brms_kinDistance_duration.rds")
```

# Formatting info
```{r}
textSize_plotTitle <- 9
textSize_plotSubtitle <- 9
textSize_axisTitle <- 9
```


# Figure 1 - Intelligibility
## Expected Posteriors
```{r}
epsilon <- 1e-5
# Generate expected predictions from the posterior
data_posterior_Int <- model_Int %>%
  tidybayes::epred_draws(
    newdata = tidyr::expand_grid(
      Severity = c("Control", "Mild", "Moderate", "Severe", "Profound"),
      condition = c("conv", "moreClear")
    ),
    re_formula = NA
  ) %>%
  dplyr::mutate(
    Severity = factor(
      Severity,
      levels = c("Control", "Mild", "Moderate", "Severe", "Profound")
    ),
    condition = factor(
      condition,
      levels = c("conv", "moreClear"),
      labels = c("conversational", "clear")
    ),
    .epred = (.epred - epsilon) / (1 - 2 * epsilon),
    # Step 1 & 2: Reverse the offset and scaling
    .epred = .epred * nrow(.) / ((nrow(.) - 1) + .5)
  )

plot_grandMean_Int <- ggplot(data_posterior_Int, 
                                   aes(x = .epred, y = Severity, 
                                       fill = condition)) +
  stat_halfeye() +
  ggokabeito::scale_fill_okabe_ito() +
  labs(x = "Predicted intelligibility rating", y = NULL,
       fill = "Condition",
       title = "Posterior Predictions") +
  scale_y_discrete(limits = rev) +
  coord_cartesian(xlim = c(0,1)) +
  theme_clean() +
  theme(legend.position = "bottom",
        axis.title = element_text(size = textSize_axisTitle),
        plot.title = element_text(size = textSize_plotTitle),
        plot.subtitle = element_text(size = textSize_plotSubtitle))
```

## ME: Group
```{r}
epsilon <- 1e-5
data_meGroup_Int <- model_Int %>%
  emmeans::emmeans( ~  Severity,
                    at = list(condition = "conv"),
                    epred = TRUE,
                    re_formula = NA,
                    ) %>%
  emmeans::contrast(method = "revpairwise") %>%
  gather_emmeans_draws() %>%
  dplyr::mutate(
    .value = (.value - epsilon) / (1 - 2 * epsilon),
    # Step 1 & 2: Reverse the offset and scaling
    .value = .value * nrow(.) / ((nrow(.) - 1) + .5),
    contrast = factor(contrast,
                      levels = c(
                        " ",
                        "Mild - Control",
                        "Moderate - Control",
                        "Severe - Control",
                        "Profound - Control"
                        #"Moderate - Mild",
                        #"Severe - Moderate",
                        #"Profound - Severe"
                      ))
  ) %>%
  dplyr::filter(!is.na(contrast))

plot_ameGroup_Int <- ggplot(data_meGroup_Int, aes(x = .value, y = contrast)) +
  geom_vline(xintercept = 0, alpha = .5) + 
  stat_halfeye(fill = ggokabeito::palette_okabe_ito(order = 7)) +
  labs(
    x = "Average marginal effect of group",
    y = NULL,
    title = "Research Question 1",
    subtitle = "Group effect (Parkinson - Control)\nat conversational."
    ) +
  scale_y_discrete(limits = rev, drop = FALSE) +
  annotate("text",x = 0, y = 6, label = "", size = 5)  + # this adds an empty annotation at the "control" line
  theme_clean() +
  theme(legend.position = "bottom",
        axis.title = element_text(size = textSize_axisTitle),
        plot.title = element_text(size = textSize_plotTitle),
        plot.subtitle = element_text(size = textSize_plotSubtitle))
plot_ameGroup_Int
```
## ME: Group x Condition
```{r}
epsilon <- 1e-5
data_meGroupCondition_Int <- model_Int %>%
  emmeans::emmeans( ~ condition | Severity,
                    #at = list(Severity = "Profound"),
                    epred = TRUE,
                    re_formula = NA,
                    ) %>%
  emmeans::contrast(method = "revpairwise") %>%
  gather_emmeans_draws() %>%
  dplyr::mutate(
    .value = (.value - epsilon) / (1 - 2 * epsilon),
    # Step 1 & 2: Reverse the offset and scaling
    .value = .value * nrow(.) / ((nrow(.) - 1) + .5)
  )

hypothesis(data_meGroupCondition_Int)
bayestestR::p_direction(data_meGroupCondition_Int)

plot_ameGroupCondition_Int <- ggplot(data_meGroupCondition_Int, aes(x = .value, y = Severity)) +
  geom_vline(xintercept = 0, alpha = .5) +
  stat_halfeye(fill = ggokabeito::palette_okabe_ito(order = 7)) +
  labs(
    x = "Average marginal effect of condition",
    y = NULL,
    title = "Research Question 2",
    subtitle = "Condition effect (clear - conversational)\nper group."
    ) +
  scale_y_discrete(limits = rev) +
  theme_clean() +
  theme(legend.position = "bottom",
        axis.title = element_text(size = textSize_axisTitle),
        plot.title = element_text(size = textSize_plotTitle),
        plot.subtitle = element_text(size = textSize_plotSubtitle))
```


## Combined
```{r}
# Combined plot
plot_Int <-  plot_grandMean_Int + plot_ameGroup_Int + plot_ameGroupCondition_Int +
  patchwork::plot_layout(ncol = 3, 
              heights = c(1)) +
  plot_annotation(title = "Intelligibility",
                  #subtitle = "Predicted intelligibility ratings across group/severity and speaking conditions.",
                  theme = theme_clean())
plot_Int

ggsave(
  plot = plot_Int,
  filename = "Plots/F1_Int.png",
  height = 5,
  width = 10,
  unit = "in",
  scale = .9,
  bg = "white"
)
```

# Figure 2 - Artic Precision
## Expected Posteriors
```{r}
# Generate expected predictions from the posterio
data_posterior_AP <- model_AP %>%
  tidybayes::epred_draws(
    newdata = tidyr::expand_grid(
      Severity = c("Control", "Mild", "Moderate", "Severe", "Profound"),
      condition = c("conv", "moreClear")
    ),
    re_formula = NA
  ) %>%
  dplyr::mutate(Severity = factor(
    Severity,
    levels = c("Control", "Mild", "Moderate", "Severe", "Profound")
  ),
  condition = factor(condition,
                     levels = c("conv","moreClear"),
                     labels = c("conversational", "clear")))

plot_grandMean_AP <- ggplot(data_posterior_AP, 
                                   aes(x = .epred, y = Severity, 
                                       fill = condition)) +
  stat_halfeye() +
  ggokabeito::scale_fill_okabe_ito() +
  labs(x = "Predicted articulatory precision rating", y = NULL,
       fill = "Condition",
       title = "Posterior Predictions") +
  scale_y_discrete(limits = rev) +
  coord_cartesian(xlim = c(0,1)) +
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
```
## ME: Group
```{r}
epsilon <- 1e-5
data_meGroup_AP <- model_AP %>%
  emmeans::emmeans( ~  Severity,
                    at = list(condition = "conv"),
                    epred = TRUE,
                    re_formula = NA,
                    ) %>%
  emmeans::contrast(method = "revpairwise") %>%
  gather_emmeans_draws() %>%
  dplyr::mutate(
    .value = (.value - epsilon) / (1 - 2 * epsilon),
    # Step 1 & 2: Reverse the offset and scaling
    .value = .value * nrow(.) / ((nrow(.) - 1) + .5),
    contrast = factor(contrast,
                      levels = c(
                        " ",
                        "Mild - Control",
                        "Moderate - Control",
                        "Severe - Control",
                        "Profound - Control"
                        #"Moderate - Mild",
                        #"Severe - Moderate",
                        #"Profound - Severe"
                      ))
  ) %>%
  dplyr::filter(!is.na(contrast))

plot_ameGroup_AP <- ggplot(data_meGroup_AP, aes(x = .value, y = contrast)) +
  geom_vline(xintercept = 0, alpha = .5) +
  stat_halfeye(fill = ggokabeito::palette_okabe_ito(order = 7)) +
  labs(
    x = "Average marginal effect of group",
    y = NULL,
    title = "Research Question 1",
    subtitle = "Group effect (Parkinson - Control)\nat conversational."
    ) +
  scale_y_discrete(limits = rev, drop = FALSE) +
  annotate("text",x = 0, y = 6, label = "", size = 5)  + # this adds an empty annotation at the "control" line
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
plot_ameGroup_AP
```
## ME: Group x Condition
```{r}
epsilon <- 1e-5
data_meGroupCondition_AP <- model_AP %>%
  emmeans::emmeans( ~ condition | Severity,
                    #at = list(Severity = "Profound"),
                    epred = TRUE,
                    re_formula = NA,
                    ) %>%
  emmeans::contrast(method = "revpairwise") %>%
  gather_emmeans_draws() %>%
  dplyr::mutate(
    .value = (.value - epsilon) / (1 - 2 * epsilon),
    # Step 1 & 2: Reverse the offset and scaling
    .value = .value * nrow(.) / ((nrow(.) - 1) + .5)
  )


plot_ameGroupCondition_AP <- ggplot(data_meGroupCondition_AP, aes(x = .value, y = Severity)) +
  geom_vline(xintercept = 0, alpha = .5) +
  stat_halfeye(fill = ggokabeito::palette_okabe_ito(order = 7)) +
  labs(
    x = "Average marginal effect of condition",
    y = NULL,
    title = "Research Question 2",
    subtitle = "Condition effect (clear - conversational)\nper group."
    ) +
  scale_y_discrete(limits = rev) +
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
```

## Combined
```{r}
# Combined plot
plot_AP <- plot_grandMean_AP + plot_ameGroup_AP + plot_ameGroupCondition_AP +
  patchwork::plot_layout(ncol = 3, 
              heights = c(1)) +
  plot_annotation(title = "Articulatory Precision",
                  #subtitle = "Predicted articulatory precision ratings across group/severity and speaking conditions.",
                  theme = theme_clean())
ggsave(
  plot = plot_AP,
  filename = "Plots/F2_AP.png",
  height = 5,
  width = 10,
  unit = "in",
  scale = .9,
  bg = "white"
)
```

# Figure 3 - VSA
## Expected Posteriors
```{r}
# Generate expected predictions from the posterior
data_posterior_aVSA <- model_aVSA %>%
  tidybayes::epred_draws(
    newdata = tidyr::expand_grid(
      Severity = c("Control", "Mild", "Moderate", "Severe", "Profound"),
      condition = c("conv", "moreClear")
    ),
    re_formula = NA
  ) %>%
  dplyr::mutate(Severity = factor(
    Severity,
    levels = c("Control", "Mild", "Moderate", "Severe", "Profound")
  ),
  condition = factor(condition,
                     levels = c("conv","moreClear"),
                     labels = c("conversational", "clear")))

plot_grandMean_aVSA <- ggplot(data_posterior_aVSA, 
                                   aes(x = .epred, y = Severity, 
                                       fill = condition)) +
  stat_halfeye() +
  ggokabeito::scale_fill_okabe_ito() +
  labs(x = "Predicted VSA (in Bark)", y = NULL,
       fill = "Condition",
       title = "Posterior Predictions") +
  scale_y_discrete(limits = rev) +
  coord_cartesian(xlim = c(0,20)) +
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
```

## ME: Group
```{r}
data_meGroup_aVSA <- model_aVSA %>%
  emmeans::emmeans( ~  Severity,
                    at = list(condition = "conv"),
                    epred = TRUE,
                    re_formula = NA,
                    ) %>%
  emmeans::contrast(method = "revpairwise") %>%
  gather_emmeans_draws() %>%
  dplyr::mutate(
    contrast = factor(contrast,
                      levels = c(
                        "",
                        "Mild - Control",
                        "Moderate - Control",
                        "Severe - Control",
                        "Profound - Control"
                        #"Moderate - Mild",
                        #"Severe - Moderate",
                        #"Profound - Severe"
                      ))
  ) %>%
  dplyr::filter(!is.na(contrast))

plot_ameGroup_aVSA <- ggplot(data_meGroup_aVSA, aes(x = .value, y = contrast)) +
  geom_vline(xintercept = 0, alpha = .5) + 
  stat_halfeye(fill = ggokabeito::palette_okabe_ito(order = 7)) +
  labs(
    x = "Average marginal effect of group",
    y = NULL,
    title = "Research Question 1",
    subtitle = "Group effect (Parkinson - Control)\nat conversational."
    ) +
  scale_y_discrete(limits = rev, drop = F) +
  annotate("text",x = 0, y = 6, label = "", size = 5)  + # this adds an empty annotation at the "control" line
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
plot_ameGroup_aVSA
```

## ME: Group x Condition
```{r}
data_meGroupCondition_aVSA <- model_aVSA %>%
  emmeans::emmeans( ~ condition | Severity,
                    #at = list(Severity = "Profound"),
                    epred = TRUE,
                    re_formula = NA,
                    ) %>%
  emmeans::contrast(method = "revpairwise") %>%
  gather_emmeans_draws()


plot_ameGroupCondition_aVSA <- ggplot(data_meGroupCondition_aVSA, aes(x = .value, y = Severity)) +
  geom_vline(xintercept = 0, alpha = .5) + 
  stat_halfeye(fill = ggokabeito::palette_okabe_ito(order = 7)) +
  labs(
    x = "Average marginal effect of condition",
    y = NULL,
    title = "Research Question 2",
    subtitle = "Condition effect (clear - conversational)\nper group."
    ) +
  scale_y_discrete(limits = rev) +
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
```


## Combined
```{r}
# Combined plot
plot_aVSA <- plot_grandMean_aVSA + plot_ameGroup_aVSA + plot_ameGroupCondition_aVSA +
  patchwork::plot_layout(ncol = 3, 
              heights = c(1)) +
  plot_annotation(title = "Acoustic Vowel Space Area (VSA)",
                  #subtitle = "Predicted VSA (in Bark) across group/severity and speaking conditions.",
                  theme = theme_clean())
ggsave(
  plot = plot_aVSA,
  filename = "Plots/F3_aVSA.png",
  height = 5,
  width = 10,
  unit = "in",
  scale = .9,
  bg = "white"
)
```
# Figure 4 - KinDistance
## Expected Posteriors
```{r}
# Generate expected predictions from the posterior
data_posterior_kinDistance <- model_kinDistance %>%
  tidybayes::epred_draws(
    newdata = tidyr::expand_grid(
      Severity = c("Control", "Mild", "Moderate", "Severe", "Profound"),
      condition = c("conv", "moreClear")
    ),
    re_formula = NA
  ) %>%
  dplyr::mutate(Severity = factor(
    Severity,
    levels = c("Control", "Mild", "Moderate", "Severe", "Profound")
  ),
  condition = factor(condition,
                     levels = c("conv","moreClear"),
                     labels = c("conversational", "clear")))

plot_grandMean_kinDistance <- ggplot(data_posterior_kinDistance, 
                                   aes(x = .epred, y = Severity, 
                                       fill = condition)) +
  stat_halfeye() +
  ggokabeito::scale_fill_okabe_ito() +
  labs(x = "Predicted kinematic distance (mm)", y = NULL,
       fill = "Condition",
       title = "Posterior Predictions") +
  scale_y_discrete(limits = rev) +
  coord_cartesian(xlim = c(0, 43)) +
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
```

## ME: Group
```{r}
data_meGroup_kinDistance <- model_kinDistance %>%
  emmeans::emmeans( ~  Severity,
                    at = list(condition = "conv"),
                    epred = TRUE,
                    re_formula = NA,
                    ) %>%
  emmeans::contrast(method = "revpairwise") %>%
  gather_emmeans_draws() %>%
  dplyr::mutate(
    contrast = factor(contrast,
                      levels = c(
                        "",
                        "Mild - Control",
                        "Moderate - Control",
                        "Severe - Control",
                        "Profound - Control"
                        #"Moderate - Mild",
                        #"Severe - Moderate",
                        #"Profound - Severe"
                      ))
  ) %>%
  dplyr::filter(!is.na(contrast))

plot_ameGroup_kinDistance <- ggplot(data_meGroup_kinDistance, aes(x = .value, y = contrast)) +
  geom_vline(xintercept = 0, alpha = .5) + 
  stat_halfeye(fill = ggokabeito::palette_okabe_ito(order = 7)) +
  labs(
    x = "Average marginal effect of group",
    y = NULL,
    title = "Research Question 1",
    subtitle = "Group effect (Parkinson - Control)\nat conversational."
    ) +
  scale_y_discrete(limits = rev, drop = F) +
  annotate("text",x = 0, y = 6, label = "", size = 5)  + # this adds an empty annotation at the "control" line
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
plot_ameGroup_kinDistance
```

## ME: Group x Condition
```{r}
data_meGroupCondition_kinDistance <- model_kinDistance %>%
  emmeans::emmeans( ~ condition | Severity,
                    #at = list(Severity = "Profound"),
                    epred = TRUE,
                    re_formula = NA,
                    ) %>%
  emmeans::contrast(method = "revpairwise") %>%
  gather_emmeans_draws()


plot_ameGroupCondition_kinDistance <- ggplot(data_meGroupCondition_kinDistance, aes(x = .value, y = Severity)) +
  geom_vline(xintercept = 0, alpha = .5) + 
  stat_halfeye(fill = ggokabeito::palette_okabe_ito(order = 7)) +
  labs(
    x = "Average marginal effect of condition",
    y = NULL,
    title = "Research Question 2",
    subtitle = "Condition effect (clear - conversational)\nper group."
    ) +
  scale_y_discrete(limits = rev) +
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
```

## Combined
```{r}
# Combined plot
plot_kinDistance <- plot_grandMean_kinDistance + plot_ameGroup_kinDistance + plot_ameGroupCondition_kinDistance +
  patchwork::plot_layout(ncol = 3, 
              heights = c(1)) +
  plot_annotation(title = "Kinematic Distance",
                  #subtitle = "Predicted kinematic distance (mm) for /aɪ/ across group/severity and speaking conditions.",
                  theme = theme_clean())
ggsave(
  plot = plot_kinDistance,
  filename = "Plots/F4_kinDistance.png",
  height = 5,
  width = 10,
  unit = "in",
  scale = .9,
  bg = "white"
)
```

# Figure 5 - KinDistance + Duration
## Expected Posteriors
```{r}

avg_duration <- mean(model_kinDistance_duration$data$duration, na.rm = T)
# Generate expected predictions from the posterior
data_posterior_kinDistance <- model_kinDistance_duration %>%
  tidybayes::epred_draws(
    newdata = tidyr::expand_grid(
      Severity = c("Control", "Mild", "Moderate", "Severe", "Profound"),
      condition = c("conv", "moreClear"),
      duration = avg_duration,
    ),
    re_formula = NA
  ) %>%
  dplyr::mutate(Severity = factor(
    Severity,
    levels = c("Control", "Mild", "Moderate", "Severe", "Profound")
  ),
  condition = factor(condition,
                     levels = c("conv","moreClear"),
                     labels = c("conversational", "clear")))

plot_grandMean_kinDistance <- ggplot(data_posterior_kinDistance, 
                                   aes(x = .epred, y = Severity, 
                                       fill = condition)) +
  stat_halfeye() +
  ggokabeito::scale_fill_okabe_ito() +
  labs(x = "Predicted kinematic distance (mm)", y = NULL,
       fill = "Condition",
       title = "Posterior Predictions") +
  scale_y_discrete(limits = rev) +
  coord_cartesian(xlim = c(0, 43)) +
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
```

## ME: Group
```{r}
data_meGroup_kinDistance <- model_kinDistance_duration %>%
  emmeans::emmeans( ~  Severity,
                    at = list(condition = "conv",
                              duration = avg_duration),
                    epred = TRUE,
                    re_formula = NA,
                    ) %>%
  emmeans::contrast(method = "revpairwise") %>%
  gather_emmeans_draws() %>%
  dplyr::mutate(
    contrast = factor(contrast,
                      levels = c(
                        "",
                        "Mild - Control",
                        "Moderate - Control",
                        "Severe - Control",
                        "Profound - Control"
                        #"Moderate - Mild",
                        #"Severe - Moderate",
                        #"Profound - Severe"
                      ))
  ) %>%
  dplyr::filter(!is.na(contrast))

plot_ameGroup_kinDistance <- ggplot(data_meGroup_kinDistance, aes(x = .value, y = contrast)) +
  geom_vline(xintercept = 0, alpha = .5) + 
  stat_halfeye(fill = ggokabeito::palette_okabe_ito(order = 7)) +
  labs(
    x = "Average marginal effect of group",
    y = NULL,
    title = "Research Question 1",
    subtitle = "Group effect (Parkinson - Control)\nat conversational."
    ) +
  scale_y_discrete(limits = rev, drop = F) +
  annotate("text",x = 0, y = 6, label = "", size = 5)  + # this adds an empty annotation at the "control" line
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
plot_ameGroup_kinDistance
```

## ME: Group x Condition
```{r}
data_meGroupCondition_kinDistance <- model_kinDistance_duration %>%
  emmeans::emmeans( ~ condition | Severity,
                    at = list(duration = avg_duration),
                    epred = TRUE,
                    re_formula = NA,
                    ) %>%
  emmeans::contrast(method = "revpairwise") %>%
  gather_emmeans_draws()

plot_ameGroupCondition_kinDistance <- ggplot(data_meGroupCondition_kinDistance, aes(x = .value, y = Severity)) +
  geom_vline(xintercept = 0, alpha = .5) + 
  stat_halfeye(fill = ggokabeito::palette_okabe_ito(order = 7)) +
  labs(
    x = "Average marginal effect of condition",
    y = NULL,
    title = "Research Question 2",
    subtitle = "Condition effect (clear - conversational)\nper group."
    ) +
  scale_y_discrete(limits = rev) +
  theme_clean() +
  theme(
    legend.position = "bottom",
    axis.title = element_text(size = textSize_axisTitle),
    plot.title = element_text(size = textSize_plotTitle),
    plot.subtitle = element_text(size = textSize_plotSubtitle)
  )
```

## Combined
```{r}
# Combined plot
plot_kinDistance <- plot_grandMean_kinDistance + plot_ameGroup_kinDistance + plot_ameGroupCondition_kinDistance +
  patchwork::plot_layout(ncol = 3, 
              heights = c(1)) +
  plot_annotation(title = "Kinematic Distance + Duration",
                  #subtitle = "Predicted kinematic distance (mm) for /aɪ/ across group/severity and speaking conditions.",
                  theme = theme_clean())
ggsave(
  plot = plot_kinDistance,
  filename = "Plots/F4_kinDistance_duration.png",
  height = 5,
  width = 10,
  unit = "in",
  scale = .9,
  bg = "white"
)
```